Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-03-03 main.tex
example of arxiv citation in footnote
update introduction/related work

% imports
\usepackage[acronym,toc,shortcuts,nonumberlist]{glossaries}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{xcolor}

@@

While the \wvtwo \fe is similar to other neural feature extraction methods, it is not yet closely studied in the literature.
Choi et al. study the feature encoder\footnote{K. Choi and E. J. Yeo, “Opening the black box of wav2vec feature encoder,” arXiv preprint arXiv:2210.15386, 2022.}.%\cite{choi2022w2v2fe}

\draft{
Comparable to other neural feature extraction methods, but not closely studied in the literature.
Maybe some references or name some works which are similar.

Highlight contributions of this paper.
}

@@

\cite{facebook2019wav2vec} uses 5 layers with kernel sizes (10, 8, 4, 4, 4) and strides which are always exactly half the kernel size.
All have 512 channels, a group normalization layer with a single group and a \relu nonlinearity.
\cite{facebook2020wav2vec2} uses seven layers with kernel sizes (10, 3, 3, 3, 3, 2, 2), strides (5, 2, 2, 2, 2, 2, 2), and a GELU activation function.
The first layer applies group normalization and finally, layer normalization and a linear projection are added.
}

>>>>

% imports
\usepackage{bibentry}
\usepackage[acronym,toc,shortcuts,nonumberlist]{glossaries}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{xcolor}

\nobibliography*  % used together with bibentry package to allow footnote bibentry citations

@@

While the \wvtwo \fe is similar to other neural feature extraction methods, it is not yet closely studied in the literature.
\cite{choi2022w2v2fe} studies the feature encoder by feeding synthesized sine waves.
The authors observe that enough temporal detail is obtained and information about fundamental frequencies is represented in the model's output.
In particular, they claim that the frequencies are distributed linearly over the Hertz scale, unlike perceptually motivated scales like the Mel scale or the Greenwood function for Gammatone features.
\draft{
Other works that analyze \wvtwo models rather focus on the large \transformer part of the network which operates at a higher level of abstraction \cite{livescu2021wav2vec_analysis}\TODO{updated version and add more papers (references in Choi et al. or Livescu et al.}.
}

\draft{
Highlight contributions of this paper.
}

@@

\cite{facebook2019wav2vec} uses 5 layers with kernel sizes (10, 8, 4, 4, 4) and strides which are always exactly half the kernel size.
All have 512 channels, a group normalization layer with a single group and a \relu nonlinearity.
\cite{facebook2020wav2vec2} uses seven layers with kernel sizes (10, 3, 3, 3, 3, 2, 2), strides (5, 2, 2, 2, 2, 2, 2), and a GELU activation function.
The first layer applies group normalization and finally, layer normalization and a linear projection are added.

\cite{asapp2022performance} investigates different settings for the \wvtwo \fe and shows that the required computation can be significantly reduced while maintaining \TODO{similar} performance.
However, this is always done in the whole \wvtwo framework and not \TODO{what is different to us?}
}
